\documentclass[12pt]{article}
\usepackage[a4paper, total={6in, 9in}]{geometry} % set page layout
\usepackage{enumitem} % use enumerate list
\pagenumbering{gobble} % remove page number
\setlist[itemize]{noitemsep} % no line separation for item lists
\date{} % no date information shown

\title{\textbf{INTRODUCTORY MEETING [AGENDA]}}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Meeting information}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Date:} 17 March 2015.\newline
\textbf{Time:} 10:00 AM.\newline
\textbf{Location:} Room 4.53, Ingkarni Wardli Building.\newline
\textbf{Attendees:}
\begin{itemize}
  \item Client: Justin Watts (Ray White Group).
  \item Project supervisor: Dr. Claudia Szabo.
  \item Team 8:
  \begin{itemize}
    \item Beldin Boskell (Chair)
    \item Kamal Arieff Ahmad Faizel (Secretary),
    \item Khanh Hoang
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Objectives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This first meeting between Ray White client and software engineering team 8 will provide an opportunity for the client and team to give a brief introduction about themselves and what they are expecting from this project. Apart from that, the agenda will be addressing questions raised by both sides regarding the project details, providing a better understanding about the project and other relevant respects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Agenda outline}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Store table cell data in variables
\def \items {\textbf{Items}}
\def \presenters {\textbf{Presenters}}
\def \time {\textbf{Time}}

\def \presenterA {Clients / Team 8}
\def \presenterB {Client}
\def \presenterC {Client / Team8}
\def \presenterD {Client / Team8}

\def \timeA {5 mins}
\def \timeB {5 mins}
\def \timeC {45 mins}
\def \timeD {5 mins}
 
\def \itemA {Welcome - Introduction}
\def \itemB {Expectations and plans from the client}
\def \itemC {
  Q/A discussions about project\newline\newline
  \emph{Pre-prepared questions from team 8:}
  \begin{enumerate} % item list
    \item What does it need to do?
    \item Is it for realtors, sellers or buyers?
    \item What device is it meant for?
    \item Should the interface be similar to another app?
    \item Desktop reporting software : Do we design or just integrate?
    \item What form are the detailed examples in, how to get them?
    \item Most important features? (Development Order)
    \item Does it need to integrate with other software?
    \item General requirements
    \begin{enumerate}[label=(\alph*)] % sub item list
      \item Photo taking requirements
      \item Reporting requirements
      \item GPS requirements
      \item Custom form requirements.
      \item Desktop integration requirements.
    \end{enumerate}	
    \item Other Questions
  \end{enumerate}
}

% Display the table
\def \itemD {Conclusion/Remark of meeting}
\renewcommand{\arraystretch}{2} % stretch row space
\begin{tabular}{|p{10cm}|p{3cm}|p{1.5cm}|}
  \hline
  \items&\presenters&\time\\
  \hline
  \itemA&\presenterA&\timeA\\
  \hline
  \itemB&\presenterB&\timeB\\
  \hline
  \itemC&\presenterC&\timeC\\
  \hline
  \itemD&\presenterD&\timeD\\
  \hline
\end{tabular}

\vspace{1cm}
\noindent Recorded By:\noindent\rule{8cm}{0.4pt} Date:\noindent\rule{4cm}{0.4pt}

\end{document}
